---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

This is my document for the Peer Assessment 1. I address the questions below with code examples.

## Loading and preprocessing the data
I set the directory and read in the source file.

```{r}
setwd("./ReproducibleResearchAssignment1")
## Read in activity data
activity <- read.cs
## I aggregate the data to calculate the sums for the steps.
sumA <- aggregate(steps ~ date ,data = activity, sum)

```
## What is mean total number of steps taken per day?
1. I draw the histogram for the total steps.
```{r}
hist(sumA$steps)
```
2. The mean and median are calculated with the code below:
```{r}
meanA <- mean(sumA$steps)
medianA <- median(sumA$steps)
```
They are: mean: 10766.19 and median: 10765

## What is the average daily activity pattern?
1. the code for the time series plot is below. Again, I aggregated the steps this time with intervals and the function, mean.
```{r}
aveI <- aggregate(steps ~ interval ,data = activity, mean)
plot(aveI$interval,aveI$steps, type = "l")
```
2. The plot shows the interval with the maximum average steps. The code below is the calculation.
```{r}

xI <- aveI$interval[which.max(aveI$steps)]

```

The interval is 835
## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
